Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
describing the line-continue symbol.

\noindent If a default type is not suitable, expression type--signatures can be specified for each parameter:

>>>>

\noindent Note that the $\hookleftarrow$ symbol denotes that two lines are actually written in a single line. If a default type is not suitable, expression type--signatures can be specified for each parameter:
